An open source scientific article

### 2022-10-12 src/tex/ms.tex
Addes vesc plot (ms.tex)

>>>>

\begin{figure}
    \script{cmc_single_clusters_vesc.py}
    \centering
    \includegraphics[width=0.49\textwidth]{figures/cmc_single_clusters_vesc.pdf}
    \caption{
        The local escape velocities $v_{\rm esc}$ of all BSCO encounters generated from the four sample \CMC\ models (colored points), plotted alongside the central density $\rho_c$ of the model (maroon), that latter of which is divided by the initial central density of the model.
        See Figure \ref{fig:cmc_single_clusters_vesc} for an explanation of the color scheme.
    }
    \label{fig:cmc_single_clusters_vesc}
\end{figure}
